A community-maintained standard library of population genetic simulations

### 2019-12-18 popSimManu.tex
minor edits to the intro

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \texttt{stdpopsim}, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community maintained catalog.
The \stdpopsim catalog currently contains four organisms: humans, 
\emph{D.~melanogaster}, \emph{A.~thaliana}, and \emph{E.~coli}. For each
organism the catalog contains details on the physical organization (e.g., chromosome structure)
of their genomes, one or more genetic maps, default population-level parameters (mutation rate,
generation time) and one or more published demographic histories. Through
either a command line interface or a simple Python API, the user can specify which
organism, genetic map, chromosome, and demographic history they are interested in simulating, and are returned
simulation output from their chosen model.

The software has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its accuracy.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate,
and have documented methods for others to contribute new modules.
We welcome new collaborators.
Below we describe the resource and give an
example of how it can be used to benchmark demographic inference methods.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\linewidth]{display_items/Figure1.pdf}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the PopSim catalog contains all information
within individual species. Information within the species level is shown here
for \emph{Homo sapiens} only. We see that \emph{H. sapiens} is associated
with a default generation time and mutation rate, that it contains within
it a representation of the physical genome, genetic maps, and as shown a
subset of the demographic models currently implemented. \textbf{B.} Caching
and automated download of genetic maps. \textbf{C.} Example code to specify
and simulate models using \stdpopsim via the API (top) or
command-line interface (bottom). \textbf{D.} Simulation output from
\stdpopsim is generated as tree sequence files that can
be manipulated and analysed with \texttt{tskit}.}
\label{fig:cartoon}
\end{center}
\end{figure}

\section*{Results}
\paragraph{The \stdpopsim library}
The central contribution of the PopSim consortium currently is \stdpopsim, a community
maintained library of empirical genome data and population genetics simulation
models, providing easy access to realistic simulations. Figure \ref{fig:cartoon} shows a graphical
representation of the structure of \stdpopsim. The package centers
on a catalog of species (Fig. \ref{fig:cartoon}A), initially consisting of humans, \emph{Drosophila},
\emph{Arabidopsis}, \emph{E. coli}, and \emph{Pongo}. A species definition consists
of two key elements.  Firstly, the library defines
some basic information about its genome, including information about chromosome
lengths, average mutation rates and so on. We also provide access to detailed
empirical information such as recombination maps, which model empirically
observed heterogeneity along chromosomes. As such maps are often large and hard
to find, we provide a mechanism to automatically download (and cache locally) a
set of previously published maps (Fig. \ref{fig:cartoon}B). For example, in humans we support the
HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps. The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which are the basis for accurate simulations
of specific historical scenarios that have influenced present-day patterns of
genetic polymorphism.

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \stdpopsim has a Python API and a user-friendly
command line interface (Fig. \ref{fig:cartoon}C), allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the “tree sequence”
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed very efficiently using the tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine. We plan to include other simulation
engines to support scenarios that cannot be modelled under the coalescent framework,
and have already implemented \texttt{SLiM} \citep{haller2019slim} as
an alternative back-end.

@@

At the time of writing, more models of human history have been implemented than for
any other organism. These models include: a simplified version of the \cite{tennessen2012evolution}
model with only the African population modeled (expansion from the ancestral
population and recent growth), the three population model of \cite{gutenkunst2009inferring}
which modeled the out-of-Africa bottleneck as well as the subsequent divergence of
the European and Asian populations, the \cite{tennessen2012evolution} two population variant of the
Gutenkunst model which did not include Asian populations, but more explicitly modeled
recent rapid human population growth, the \cite{browning2018ancestry} admixture model
for American populations that models ancestral African, European, and Asian population
components, and the three-population out-of-Africa model from \cite{ragsdale2019models} that includes archaic admixture
. Together these models
contain features believed to have widespread impacts in real data (e.g. bottlenecks, population growth,
admixture) which are therefore highly pertinent in the context of method development.

For non-human genomes we have have implemented two demographic histories for
\emph{Drosophila melanogaster} and one each from \emph{A. thaliana} and \emph{E. coli}.
For \emph{D. melanogaster} we have implemented the three-epoch model estimated by \cite{sheehan2016deep} from
an African sample, as well as the out-of-Africa divergence
and associated bottleneck model of \cite{li2006inferring} which jointly models African
and European populations. For \emph{Arabidopsis thaliana}, we implemented the
model from in \cite{durvasula2017african} inferred using \MSMC. This model includes
a continuous change in population size over time, rather than pre-specified epochs of different
population sizes.

@@

We start by comparing popular methods for estimating
population size histories ($N(t)$) of single populations and subsequently
show simple examples of multi-population inference.
To evaluate and compare the performance of inference methods we developed
\texttt{snakemake} \citep{koster2012snakemake} workflows that allow reproducibility
in comparing inference methods which are available from \url{https://github.com/popgensims/analysis}
. The workflows allow efficient computing in multicore environments or on
cluster environments.

For single-population population size histories, we compared
\MSMC~\citep{schiffels2014inferring}, \smcpp~\citep{terhorst2017robust}, and
\stairwayplot~\citep{liu2015exploring}
 on simulated genomes sampled from a single population,
in a number of the \stdpopsim models described above. The pipeline was generalized to
run $R$ replicates with $C$ chromosomes for $n$ samples, for a total of $R \times C$
simulations for each demographic model. After simulation, the pipeline prepares
input files for each of the respective inference methods by grouping all
chromosomes, for each sample, into a single file. For each of the $R$ simulation replicates, this step results in an
input file for each of the
respective inference methods and derived from the same simulated tree sequences.
Each of the inference programs are then run in parallel, followed by plotting of
$N(t)$ estimates from each program.

@@

We performed demographic analysis for one-and two-population tasks.
Our one population task was to infer historical population size over
time ($N(t)$). This was done using three software packages \stairwayplot
which uses site frequency spectrum information only \citep{liu2015exploring},
the SMC based \MSMC~\citep{schiffels2014inferring} which we ran with two different
sample sizes $n\in (2 , 8)$, and \smcpp~\citep{terhorst2017robust}
which combines information from the site frequency spectrum with
recombination information as in SMC-based methods. No attempt
was made at trying to optimize the analysis from
any particular software package in present case,
as our goal was not to benchmark performance of methods but
instead show how such benchmarking could be easily done using
the \stdpopsim resource. In this spirit we ran each software package as near
to default parameters as possibile in each case. For \stairwayplot we
set the parameters numRuns=1 and dimFactor=5000. For \smcpp we used the
``estimate" run mode to infer $N(t)$ with all other parameters set
to their default values. For \MSMC we used the ``--fixedRecombination"
option and used the default number of iterations.

For the single population task we ran human (HomSap) simulations
using a variety of models: OutOfAfricaArchaicAdmixture\_5R19, OutOfAfrica\_3G09,
a constant-sized generic model, and a two-epoch generic model where the
population size instantaneously decreases from $N=10^4$ to $N=10^3$ 500
generations before the present. Each HomSap simulation was run
using the HapmapII\_GRCh37 genetic maps. For \emph{D. melanogaster}
we estimated $N(t)$ from an African sample simulated under the DroMel,
African3Epoch\_1S16 model using the Comeron2012\_dm6 map. Finally we ran
simulations of \emph{A. thaliana} genomes using the AraTha African2Epoch\_1H18
model under the Salome2012\_TAIR7 map. For each model, 3 replicate whole genomes were
simulated and the population size estimated from those data. In all cases we
set the sample size of the focal population to $N=50$ chromosomes.

Following simulation, low-recombination portions of chromosomes were masked
from the analysis in a manner that reflects the ``accessible" subset of sites
used in empirical population genomic studies \citep[e.g.,][]{danecek20111000,langley2012genomic}.
Specifically we masked regions of 1cM or greater in the lowest 5th percentile of the empirical
distribution of recombination, regions which are nearly uniformly absent for
empirical analysis.

@@

To conduct inference on these models, we used three commonly used methods:
\dadi~\citep{gutenkunst2009inferring}, \fastsimcoal2~\citep{excoffier2013robust},
and \smcpp~\citep{terhorst2017robust}. As above, these methods were used
generally with default settings and we did not attempt to optimize their performance or fit
parameter-rich demographic models. As with the single population inference pipeline,
we developed a \texttt{snakemake}~\citep{koster2012snakemake} workflow to manage
our inference pipeline and maintain reproducibility.

For both \dadi and \fastsimcoal2, we fit a two population
isolation-with-migration (IM) model with constant population sizes to the simulated
data from the HomSap and DroMel models. This IM model contains six parameters:
the ancestral population size, the size of population 1 after the split, the size of
population 2 after the split, the divergence time, and two migration rate parameters.
Importantly, this meant that for both species, the
fitted model did not match the simulated model (Figure \ref{fig:IM_popn_human}C and Sx).
In the HomSap case, we therefore performed inference solely on the Africa
and Europe populations, meaning that the Asia population functioned as a ghost
population that was ignored by our inference. Our motivation for fitting this simple
IM model was to mimic the typical approach of two population inference on empirical
data, where the user is not aware of the `true' underlying demography and the inference
model is often misspecified. To ground-truth our inference approach, we also conducted
inference on a generic IM model that was identical to the model used for inference.

@@

Following simulation, we outputted tree sequences and masked low-recombination
regions using the same approach described for the single population pipeline above. We
converted tree sequences into a two-dimensional site frequency spectrum for all
chromosomes in the appropriate format for \dadi and \fastsimcoal2. For each simulation
replicate, we performed 10 runs of \dadi and \fastsimcoal2 and checked for convergence.
Detailed settings for \dadi and \fastsimcoal2 can be found in the Snakefile
on the popgensims/analysis GitHub repository (\url{https://github.com/popgensims/analysis}).
The parameter estimates from the top run from each simulation replicate
are shown in Figures \ref{fig:IM_popn_human}C and Sx.

For \smcpp , we converted the tree sequences into vcf format and performed inference
with default settings. Importantly, \smcpp assumes no migration post-divergence, so
here again the inference model does not exactly match the simulated model for the
human model that does include migration. However, because \smcpp allows
for continuous population size changes, it is better equipped to capture many of the
more complex aspects of the simulated demographic models (e.g., exponential growth).

To visualize our results, we plotted the inferred population size trajectories
for each simulation replicate along side the true (census) population sizes
(Figures \ref{fig:IM_popn_human}C Sx). Here, unlike the single population pipeline,
we focus on census size rather than the inverse coalescence rate as the `true' population size.

@@

\pagebreak
\beginsupplement
\section*{Supplemental Figures}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Gutenkunst.pdf}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \stairwayplot,
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{gutenkunst2009inferring} model and using the genetic map
inferred in \cite{international2007second}. From top to bottom we show estimates for each
of the three populations in the model YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_gutenkunst}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/d_mel_two_popn_comp.png}
\caption{\textbf{A comparison two-population parameter estimates in \emph{Drosophila}}. Here we show estimates of $N(t)$ inferred using \dadi, \texttt{fastsimcoal2}, or \smcpp.
Data were generated by simulating
replicate human genomes under the \cite{li2006inferring} model and using the genetic map
inferred in \cite{comeron2012many}. See legend of Figure \ref{fig:IM_popn_human} for details.
In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:two_popn_fly}
\end{center}
\end{figure}

>>>>

For these reasons, we have generated a standardized, community-driven resource
for simulating published demographic models from a number of popular study systems.
This resource, which we call \texttt{stdpopsim}, makes running
realistic simulations for population genetic analysis a simple matter of
choosing pre-implemented models from a community maintained catalog.
The \stdpopsim catalog currently contains five organisms: humans, orangutans,
\emph{D.~melanogaster}, \emph{A.~thaliana}, and \emph{E.~coli}. For each
organism the catalog contains details on the physical organization (e.g., chromosome structure)
of their genomes, one or more genetic maps, default population-level parameters (mutation rate,
generation time) and one or more published demographic histories. Through
either a command line interface or a simple Python API, the user can specify which
organism, genetic map, chromosome, and demographic history they are interested in simulating, and the
simulation output from their chosen model is returned.

The software has been developed by the PopSim Consortium using a
distributed open source model, with strong procedures in place
to continue its growth and maintain its accuracy.
Importantly, we have rigorous quality control methods to ensure implemented models are accurate,
and have documented methods for others to contribute new modules.
We invite new collaborators to join our community.
Below we describe the resource and give an
example of how it can be used to benchmark demographic inference methods.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\linewidth]{display_items/Figure1.pdf}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the PopSim catalog contains all information
within individual species. Information within the species level is shown here
for \emph{Homo sapiens} only. We see that \emph{H. sapiens} is associated
with a default generation time and mutation rate,
a representation of the physical genome, and two genetic maps. Also shown is a
subset of the demographic models currently implemented. \textbf{B.} Caching
and automated download of genetic maps. \textbf{C.} Example code to specify
and simulate models using \stdpopsim via the API (top) or
command-line interface (bottom). \textbf{D.} Simulation output
is a tree sequence file that can
be manipulated and analysed with \tskit.}
\label{fig:cartoon}
\end{center}
\end{figure}

\section*{Results}
\paragraph{The \stdpopsim library}
The central contribution of the PopSim consortium currently is \stdpopsim, a
community-maintained library of empirical genome data and population genetics simulation
models, providing easy access to realistic simulations. Figure \ref{fig:cartoon} shows a graphical
representation of the structure of \stdpopsim. The package centers
on a catalog of species (Fig. \ref{fig:cartoon}A), initially consisting of humans, \emph{Drosophila},
\emph{Arabidopsis}, \emph{E. coli}, and \emph{Pongo}. A species definition consists
of two key elements.  Firstly, the library defines
some basic information about the species' genome, including information about chromosome
lengths, average mutation rates and so on. We also provide access to detailed
empirical information such as recombination maps, which model empirically-observed
heterogeneity along chromosomes. As such maps are often large and hard
to find, we provide a mechanism to automatically download (and cache locally) a
set of previously published maps (Fig. \ref{fig:cartoon}B). For example, in humans we support the
HapMapII~\citep{international2007second} and
deCODE~\citep{kong2010fine} genetic maps. The second key element of a species description
within \stdpopsim is a set of carefully curated population genetic model
descriptions from the literature, which are the basis for accurate simulations
of specific historical scenarios that have influenced present-day patterns of
genetic polymorphism.

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \stdpopsim has a Python API and a user-friendly
command line interface (Fig. \ref{fig:cartoon}C), allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the “tree sequence”
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed very efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine. We plan to include other simulation
engines to support scenarios that cannot be modelled under the coalescent framework,
and have already implemented \texttt{SLiM} \citep{haller2019slim} as
an alternative back-end.

@@

At the time of writing, more models of human history have been implemented than for
any other organism. These models include: a simplified version of the \cite{tennessen2012evolution}
model with only the African population specified (expansion from the ancestral
population and recent growth), the three population model of \cite{gutenkunst2009inferring}
which specifies the out-of-Africa bottleneck as well as the subsequent divergence of
the European and Asian populations, the \cite{tennessen2012evolution} two population variant of the
Gutenkunst model which does not include Asian populations, but more explicitly models
recent rapid human population growth, the \cite{browning2018ancestry} admixture model
for American populations which specifies ancestral African, European, and Asian population
components, and the three-population out-of-Africa model from \cite{ragsdale2019models}
which includes archaic admixture.
Together these models
contain features believed to have widespread impacts in real data (e.g. bottlenecks, population growth,
admixture), and are therefore highly pertinent in the context of method development.

For non-human genomes we have have implemented two demographic histories for
\emph{Drosophila melanogaster} and one each from \emph{A. thaliana} and \emph{E. coli}.
For \emph{D. melanogaster} we have implemented the three-epoch model estimated by \cite{sheehan2016deep} from
an African sample, as well as the out-of-Africa divergence
and associated bottleneck model of \cite{li2006inferring} which jointly models African
and European populations. For \emph{Arabidopsis thaliana}, we implemented the
model in \cite{durvasula2017african} inferred using \MSMC. This model includes
a continuous change in population size over time, rather than pre-specified epochs of different
population sizes.

@@

We start by comparing popular methods for estimating
population size histories ($N(t)$) of single populations and subsequently
show simple examples of multi-population inference.
To reproducibly evaluate and compare the performance of inference methods, we developed
\texttt{snakemake} \citep{koster2012snakemake} workflows,
available from \url{https://github.com/popgensims/analysis}.
These workflows allow efficient computing in multicore or cluster environments.

For single-population population size histories, we compared
\MSMC~\citep{schiffels2014inferring}, \smcpp~\citep{terhorst2017robust}, and
\stairwayplot~\citep{liu2015exploring}
 on simulated genomes sampled from a single population,
in a number of the demographic models described above. The pipeline was generalized to
run $R$ replicates with $C$ chromosomes for $n$ samples, for a total of $R \times C$
simulations for each demographic model. After simulation, the pipeline prepares
input files for each of the respective inference methods by grouping all
chromosomes, for each sample, into a single file. For each of the $R$ simulation replicates, this step results in an
input file for each of the
respective inference methods and derived from the same simulated tree sequences.
Each of the inference programs are then run in parallel, followed by plotting of
$N(t)$ estimates from each program.

@@

We performed demographic analysis for one-and two-population tasks.
Our one population task was to infer historical population size over
time ($N(t)$). This was done using three software packages: \stairwayplot
which uses site frequency spectrum information only \citep{liu2015exploring};
the SMC based \MSMC~\citep{schiffels2014inferring} which we ran with two different
sample sizes $n\in (2 , 8)$; and \smcpp~\citep{terhorst2017robust},
which combines information from the site frequency spectrum, with
recombination information as in SMC-based methods. No attempt
was made at trying to optimize the analysis from
any particular software package,
as our goal was not to benchmark performance of methods but
instead show how such benchmarking could be easily done using
the \stdpopsim resource. In this spirit we ran each software package as near
to default parameters as possibile. For \stairwayplot we
set the parameters numRuns=1 and dimFactor=5000. For \smcpp we used the
``estimate" run mode to infer $N(t)$ with all other parameters set
to their default values. For \MSMC we used the ``--fixedRecombination"
option and used the default number of iterations.

For the single-population task we ran human (HomSap) simulations
using a variety of models: OutOfAfricaArchaicAdmixture\_5R19, OutOfAfrica\_3G09,
a constant-sized generic model, and a two-epoch generic model where the
population size instantaneously decreases from $N=10^4$ to $N=10^3$, 500
generations before the present. Each HomSap simulation was run
using the HapmapII\_GRCh37 genetic maps. For \emph{D. melanogaster}
we estimated $N(t)$ from an African sample simulated under the DroMel,
African3Epoch\_1S16 model using the Comeron2012\_dm6 map. Finally we ran
simulations of \emph{A. thaliana} genomes using the AraTha African2Epoch\_1H18
model under the Salome2012\_TAIR7 map. For each model, three replicate whole genomes were
simulated and the population size estimated from those data. In all cases we
set the sample size of the focal population to $N=50$ chromosomes.

Following simulation, low-recombination portions of chromosomes were masked
from the analysis in a manner that reflects the ``accessible" subset of sites
used in empirical population genomic studies \citep[e.g.,][]{danecek20111000,langley2012genomic}.
Specifically we masked regions of 1\,cM or greater in the lowest 5th percentile of the empirical
distribution of recombination, regions which are nearly uniformly absent for
empirical analysis.

@@

To conduct inference on these models, we applied three commonly used methods:
\dadi~\citep{gutenkunst2009inferring}, \fastsimcoal2~\citep{excoffier2013robust},
and \smcpp~\citep{terhorst2017robust}. As above, these methods were used
generally with default settings and we did not attempt to optimize their performance or fit
parameter-rich demographic models. As with the single population inference pipeline,
we developed a \texttt{snakemake}~\citep{koster2012snakemake} workflow to manage
our inference pipeline and maintain reproducibility.

For both \dadi and \fastsimcoal2, we fit a two population
isolation-with-migration (IM) model, with constant population sizes, to the simulated
data from the HomSap and DroMel models. This IM model contains six parameters:
the ancestral population size, the size of population 1 after the split, the size of
population 2 after the split, the divergence time, and two migration rate parameters.
Importantly, this meant that for both species, the
fitted model did not match the simulated model (Figures \ref{fig:IM_popn_human} and \ref{fig:two_popn_fly}).
In the HomSap case, we therefore performed inference solely on the Africa
and Europe populations, meaning that the Asia population functioned as a ghost
population that was ignored by our inference. Our motivation for fitting this simple
IM model was to mimic the typical approach of two population inference on empirical
data, where the user is not aware of the `true' underlying demography and the inference
model is often misspecified. To ground-truth our inference approach, we also conducted
inference on a generic IM model that was identical to the model used for inference.

@@

Following simulation, we outputted tree sequences and masked low-recombination
regions using the same approach described for the single population pipeline above. We
converted tree sequences into a two-dimensional site frequency spectrum for all
chromosomes in the appropriate format for \dadi and \fastsimcoal2. For each simulation
replicate, we performed 10 runs of \dadi and \fastsimcoal2 and checked for convergence.
Detailed settings for \dadi and \fastsimcoal2 can be found in the Snakefile
on the popgensims/analysis GitHub repository (\url{https://github.com/popgensims/analysis}).
The parameter estimates from the top run of each simulation replicate
are shown in Figures \ref{fig:IM_popn_human}C and \ref{fig:two_popn_fly}C.

For \smcpp , we converted the tree sequences into vcf format and performed inference
with default settings. Importantly, \smcpp assumes no migration post-divergence, so
here again the model fitted during inference does not exactly match the simulated
human demography that does include migration. However, because \smcpp allows
for continuous population size changes, it is better equipped to capture many of the
more complex aspects of the simulated demographic models (e.g., exponential growth).

To visualize our results, we plotted the inferred population size trajectories
for each simulation replicate along side the true (census) population sizes
(Figures \ref{fig:IM_popn_human}C and \ref{fig:two_popn_fly}C). Here, unlike the single-population pipeline,
we focus on census size rather than the inverse coalescence rate as the `true' population size.

@@

\pagebreak
\beginsupplement
\section*{Supplemental Figures}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Gutenkunst.pdf}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \stairwayplot,
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{gutenkunst2009inferring} model and using the genetic map
inferred in \cite{international2007second}. From top to bottom we show estimates for each
of the three populations in the model: YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_gutenkunst}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/d_mel_two_popn_comp.png}
\caption{\textbf{Parameters estimated using a two-population \emph{Drosophila} model}.
Here we show estimates of $N(t)$ inferred using \dadi, \texttt{fastsimcoal2}, or \smcpp.
Data were generated by simulating
replicate \emph{Drosophila} genomes under the \cite{li2006inferring} model and using the genetic map
inferred in \cite{comeron2012many}. See legend of Figure \ref{fig:IM_popn_human} for details.
In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:two_popn_fly}
\end{center}
\end{figure}
